Effects of Reynolds Number on the Performance and Near-Wake of a Cross-Flow Turbine

### 2014-06-17 paper.tex
Add wake characteristics subsubsections and defs for derivative mathrms

@@

@@

>>>>

\def \p{\partial}
\def \d{\mathrm{d}}
\def \D{\mathrm{D}}

@@

\todo[inline]{Put asymptotic behavior here.}

@@

\todo[inline]{Plot asymptotic behavior for a bunch of locations all on the same
plot.}

\subsubsection{Mean Kinetic Energy Transport}

The relative importance of various physical processes on mean kinetic energy
transport/recovery in the streamwise direction $\p K / \p x$ are plotted in...

\todo[inline]{Recreate the kinetic energy bar graph for all $Re$.}
